Global well-being and mental health in the internet age

### 2022-08-17 ms.Rmd
Improve outputs

csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(ragg)
library(khroma)
library(labelled)
library(countrycode)
library(plotly)
library(lubridate)
library(kableExtra)
library(brms)
library(knitr)
library(here)
library(posterior)
library(bayestestR)
library(gtsummary)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(ggstance)
library(tidybayes)
library(ggdist)
library(DT)
library(tidyverse)

@@

# Create directory for intermediate files
dir.create(here("data"), FALSE)

@@

ggplotly(p1, tooltip = "text") %>% 
  layout(
    margin = list(t = 100, r = 100, b = 100, l = 100)
  ) %>% 
  htmlwidgets::saveWidget("Figure-1-interactive.html")
```

@@

# Save interactive table to country-table.html
tab %>% 
  mutate(
    Country = relevel(factor(Country), ref = "World"),
    d_nhst = factor(d_nhst),
    d_rope = factor(d_rope)
  ) %>% 
  datatable(filter = "top", rownames = FALSE) %>% 
  formatRound(4:12, 3) %>% 
  saveWidget("country-table.html", title = "Country-specific parameters")
```

>>>>

csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

```{r setup, include = FALSE}
# Packages
library(papaja)
library(readxl)
library(imputeTS)
library(naniar)
library(scales)
library(janitor)
library(haven)
library(ragg)
library(khroma)
library(labelled)
library(countrycode)
library(plotly)
library(lubridate)
library(kableExtra)
library(brms)
library(knitr)
library(here)
library(posterior)
library(bayestestR)
library(gtsummary)
library(kableExtra)
library(memoise)
library(cachem)
library(ggh4x)
library(cmdstanr)
library(ggstance)
library(tidybayes)
library(ggdist)
library(DT)
library(htmlwidgets)
library(tidyverse)

@@

# Create directory for intermediate and output files
dir.create(here("data"), FALSE)
dir.create(here("Output"), FALSE)

@@

ggplotly(p1, tooltip = "text") %>% 
  layout(
    margin = list(t = 100, r = 100, b = 100, l = 100)
  ) %>% 
  saveWidget("Output/Figure-1.html")
```

@@

# Save interactive table
tab %>% 
  mutate(
    Country = relevel(factor(Country), ref = "World"),
    d_nhst = factor(d_nhst),
    d_rope = factor(d_rope)
  ) %>% 
  datatable(filter = "top", rownames = FALSE) %>% 
  formatRound(4:12, 3) %>% 
  saveWidget("Output/Table-S2.html", title = "Country-specific parameters")
```
